### 2017-11-06 1/exams/m2.tex
Solution to m2.

\censorruleheight=0ex
%\StopCensoring

@@

(define (f b s) s)
(define (g fs) (fs #false))
(define (h bs ns) 2)
(define (i f) (f 2))
(define (j f xs) (map f xs))
(define (k f g x) (g (f x)))
\end{SaveVerbatim}

@@

;; avg : [Listof Number] -> Number
;; Compute the average of a list of numbers
;; Assume: the list is non-empty
(check-expect (avg (list 3 4 5)) 4)
(check-expect (avg (list 10 20)) 15)
(define (avg lon)
  (/ (sum lon) 
     (length lon)))

;; sum : [Listof Number] -> Number
;; Sum the list of numbers
(check-expect (sum '()) 0)
(check-expect (sum (list 3 4 5)) 12)
(define (sum lon)
  (foldr + 0 lon))

;; Alt: follow [Listof Number] template
\end{SaveVerbatim}

@@

@@

@@

;; ans : CYOA [Listof Boolean] -> CYOA
;; ...
(check-expect (adv a0 (list #true #false)) "A0")
(check-expect (adv a1 (list #true #false)) "A1")
(check-expect (adv a2 (list #false #true)) "A1")
(check-expect (adv a2 (list #false)) a1)
(define (ans adv loa)
  (cond [(string? adv) adv]
        [(empty? loa) adv]
        [(first loa)
         (ans (choice-yes adv) (rest adv))]
        [else
         (ans (choice-no adv) (rest adv))]))
\end{SaveVerbatim}

>>>>

\censorruleheight=0ex
\StopCensoring

@@

(check-expect (lookup "a" '()) #false)
(check-expect (lookup "a" (list (list "a" "b"))) "b")
(check-expect (lookup "a" (list (list "c" "b") (list "a" "d"))) "d")
(define (lookup w d)
  (cond [(empty? d) #false]
        [(cons? d)
         (if (string=? (first (first d)) w)
             (second (first d))
             (lookup w (rest d)))]))

@@

;; w-avg : [Listof Number] [Listof Number] -> Number
;; Compute the weighted average of a list of numbers and weights
;; Assume: lists have the same length (and non-empty)
(check-expect (w-avg (list 70 80 90) (list 1 1 2)) 82.5)
(define (w-avg lon ws)
  (/ (w-sum lon ws) 
     (foldr + 0 ws)))

;; w-sum : [Listof Number] [Listof Number] -> Number
;; Sum the list of numbers according to given weights
;; Assume: lists have same length
(check-expect (w-sum (list 70 80 90) (list 1 1 2)) (+ 70 80 180))
(define (w-sum lon ws)
  (cond [(empty? lon) 0]
        [(cons? lon)
         (+ (* (first lon) (first ws))
            (w-sum (rest lon) (rest ws)))]))

;; Alt: define w-total function for denominator

;; w-total : [Listof Number] -> Number
;; Total a list of weights
(define (w-total ws)
  (cond [(empty? ws) 0]
        [(cons? ws)
         (+ (first ws) 
            (w-total (rest ws)))]))
\end{SaveVerbatim}

@@

\vspace{1em}
\noindent
[Provide your answer on the next page.]

@@

\noindent
[Space for problem 4.]

@@

;; ans : CYOA [Listof Boolean] -> CYOA
;; Compute the remaining adventure after using answers from list
(check-expect (adv a0 (list #true #false)) "A0")
(check-expect (adv a1 (list #true #false)) "A1")
(check-expect (adv a2 (list #false #true)) "A1")
(check-expect (adv a2 (list #false)) a1)
(define (ans adv loa)
  (cond [(string? adv) adv]
        [(empty? loa) adv]
        [(cons? loa)
         (if (first loa)
             (ans (choice-yes adv) (rest adv))
             (ans (choice-yes adv) (rest adv)))]))
\end{SaveVerbatim}
